Co-moving stars in \textsl{Gaia DR1}: a catalog of genuine co-moving star pairs from low-resolution spectroscopic follow-up

### 2017-05-18 paper/comoving-followup.tex
notes

% Project-specific
\newcommand{\gaia}{\project{Gaia}}

@@

\author{David~W.~Hogg}
\affiliation{todo}

@@

@@

Outline:
- Stars form in clusters, chemically homogeneous at some level
- Clusters generally disrupt slowly through a process that preserves initial
  clustering in conserved quantities but destroys phase coherence
- Most significant process is probably tidal heating
- Dissolved clusters are therefore useful dynamical tracers of mass distribution
- In Galactic halo, globular clusters
- In disk, hope is to use chemical signatures to connect stars, then can use
  dynamics to reconstruct birth clusters, infer mass distribution / evolution
- Clusters have advantage of many stars per cluster, but fewer clusters
- Wide binary stars are little potentiometers themselves - only N=2, but are far
  more numerous as a population
- Long-term goal is to study the separation distribution of wide-binaries as a
  function of age and Galactic orbit distribution (disk vs. halo)
    - Is there a separation truncation?
    - Can that be described just from Galactic tides, or need perturbers?
- Also useful for stellar models: should have same age, chemistry, but need to
  test this
    - Chemical homogeneity tested with few open clusters - wide binaries another
      test
    - Need sample of confirmed widely-separated binaries, follow-up to get
      detailed abundances
    - Need way to verify that widely separated stars are physically associated,
      via kinematics

@@

@@

\acknowledgements
...

>>>>

% Project-specific
\newcommand{\gaia}{\project{Gaia}}
\newcommand{\DR}[1]{\acronym{DR}1}
\newcommand{\tgas}{\acronym{TGAS}}

@@

@@

% \author{David~W.~Hogg}
% \affiliation{todo}

@@

Outline:
- Stars form in clusters, chemically homogeneous at some level
- Clusters generally disrupt slowly through a process that preserves initial
  clustering in conserved quantities but destroys phase coherence
- Most significant process is probably tidal heating
- Dissolved clusters are therefore useful dynamical tracers of mass distribution
- In Galactic halo, globular clusters
- In disk, hope is to use chemical signatures to connect stars, then can use
  dynamics to reconstruct birth clusters, infer mass distribution / evolution
- Clusters have advantage of many stars per cluster, but fewer clusters
- Wide binary stars are little potentiometers themselves - only N=2, but are far
  more numerous as a population
- Long-term goal is to study the separation distribution of wide-binaries as a
  function of age and Galactic orbit distribution (disk vs. halo)
    - Is there a separation truncation?
    - Can that be described just from Galactic tides, or need perturbers?
- Also useful for stellar models: should have same age, chemistry, but need to
  test this
    - Chemical homogeneity tested with few open clusters - wide binaries another
      test
    - Need sample of confirmed widely-separated binaries, follow-up to get
      detailed abundances
    - Need way to verify that widely separated stars are physically associated,
      via kinematics
- Some bullshit about Gaia, TGAS, etc., released as a part of \gaia\ \DR{1}\

@@

The wide-separation co-moving stars presented later in this work were originally
identified as candidate co-moving stars in a search of the \tgas\ catalog.

@@

\acknowledgements
David W. Hogg (NYU)
